Expressive, Modular and Compositional Embedded DSLs

### 2015-05-04 dAlg/mrm.tex
Thoughts

\title{Modular and Dependent Interpretations for Shallow Embeddings}
%\title{Composable Algebra with Dependencies}

@@

\begin{abstract}

@@

>>>>

\title{Expressive, Modular and Compositional Embedded DSLs}
\subtitle{(Functional Pearl)}

@@

\begin{abstract}
Compositionality is a desirable characteristic for the semantics of
DSLs. In functional programming folds are used to enforce
compositionality. However folds make certain compositional
interpretations hard to express modularly. This pearl presents a
simple technique that allows non-trivial, but compositional
interpretations of DSLs to be expressed in a fully modular way
using folds.

\begin{comment}

@@

\end{comment}
